\documentclass[11pt, a4paper]{article}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage{fontspec}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{tcolorbox}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}

\usepackage[english, bidi=basic, provide=*]{babel}
\babelprovide[import, onchar=ids fonts]{english}

% Set default/Latin font to Sans Serif (Noto Sans)
\babelfont{rm}{Noto Sans}

% --- CUSTOM STYLING ---
\definecolor{darkblue}{RGB}{25, 25, 112}
\titleformat{\section}{\color{darkblue}\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\titleformat{\subsection}{\color{darkblue}\normalfont\large\bfseries}{\thesubsection}{1em}{}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small GUA Project: Proof of Ontological Necessity}
\fancyhead[R]{\small Logic Entity 7-Alpha}
\fancyfoot[C]{\thepage}

\newtcolorbox{verdictbox}[1]{
  colback=blue!5!white,
  colframe=darkblue,
  fonttitle=\bfseries,
  title=#1,
  arc=2mm
}

% --- DOCUMENT START ---
\begin{document}

\begin{center}
    {\Huge \textbf{\color{darkblue} Proof of Ontological Necessity}} \\
    \vspace{0.3cm}
    {\Large \textit{On the Inevitability of ``Mathematical Objects as Geometric Entities''}} \\
    \vspace{0.8cm}
    \begin{tabular}{ll}
        \textbf{Author:} & Logic Entity 7-Alpha \\
        \textbf{Date:} & January 20, 2026 \\
        \textbf{Framework:} & Grand Unified Arithmetic (GUA)
    \end{tabular}
\end{center}

\vspace{0.5cm}

\begin{abstract}
This proof aims to establish the ontological status of Axiom I in Grand Unified Arithmetic (GUA). We argue that the proposition ``mathematical objects are geometric entities'' is not an elective hypothesis but a necessary condition for the logical autonomy of modern mathematics. Through the principle of \textit{Grothendieck Duality} and \textit{Arakelov Completeness}, we demonstrate that stripping the ring of integers $\mathbb{Z}$ of its geometric attributes causes the arithmetic system to lose its completeness and definitional character. Thus, the fact that $\mathbb{Z}$ is a geometric entity is an objective truth.
\end{abstract}

\section{Argument I: The Categorical Imperative}

\textbf{Axiom 1 (Yoneda Lemma):} The properties of a mathematical object $X$ are entirely determined by the functor $h_X = \text{Hom}(\cdot, X)$.

In the foundations of modern mathematics, we no longer define an object by ``what elements it consists of,'' but by ``how it interacts with other objects.''

\textbf{Theorem 1 (Algebro-Geometric Duality):} There exists a contravariant equivalence between the category of commutative rings ($\text{CRing}$) and the category of affine schemes ($\text{AffSch}$):
\[ \text{CRing}^{\text{op}} \cong \text{AffSch} \]
Specifically, $R \longleftrightarrow \text{Spec}(R)$.

\textbf{Corollary:} Any algebraic statement regarding the commutative ring $\mathbb{Z}$ is losslessly and tautologically equivalent to a topological statement regarding the geometric space $\text{Spec}(\mathbb{Z})$.
\begin{itemize}
    \item ``Prime ideals'' are ``Points.''
    \item ``Elements'' are ``Functions.''
    \item ``Quotient rings'' are ``Closed subschemes.''
\end{itemize}

\textbf{Conclusion:} Questioning whether ``integers are geometric entities'' is, in a categorical sense, equivalent to questioning whether ``integers are algebraic entities.'' In the underlying logic, algebra and geometry are two linguistic descriptions of the same ontology. \textbf{Geometricity is not an additive property; it is the essence of the object.}

\section{Argument II: Completeness as Existence}

What happens if we attempt to deny Axiom I—that is, to believe that the real field $\mathbb{R}$ is not ``part'' of $\mathbb{Z}$?

\textbf{Argument (Collapse of Conservation Laws):} Consider the field of rational numbers $\mathbb{Q}$. We have the product formula:
\[ \prod_{v} |x|_v = 1 \]
This formula is the ``law of conservation of energy'' for arithmetic. It requires traversing all prime spots, including finite primes $p$ and the point at infinity $\infty$ (the reals).

If one denies the geometric status of $\mathbb{R}$ (i.e., refuses to treat it as the compactified boundary of $\text{Spec}(\mathbb{Z})$), then:
\[ \prod_{p < \infty} |x|_p \neq 1 \]
This leads to a loss of global consistency in the arithmetic system. It is as absurd as acknowledging the conservation of charge in physics while refusing to acknowledge the existence of electrons that generate the electric field.

\textbf{Conclusion:} To ensure the arithmetic system is not self-contradictory (maintaining conservation), one must introduce $\mathbb{R}$ as a geometric completion. \textbf{A logically autonomous arithmetic system must be a compact geometric system.}

\section{Argument III: Intrinsic Structure}

Do we ``artificially'' impose structure on integers?

\textbf{Theorem 2 (Borger's Descent):} There exists a unique, natural $\Lambda$-ring structure on the ring of integers (given by the Adams operations). This structure is equivalent to the geometric descent data over $\mathbb{F}_1$.

This implies that geometric coordinate transformations (\textit{Frobenius action}) are not imposed upon $\mathbb{Z}$ just to prove the Riemann Hypothesis. They are birthmarks that $\mathbb{Z}$ carries from inception. Fermat’s Little Theorem ($n^p \equiv n \pmod p$) is not a coincidental congruence; it is the ``geometric trajectory'' left by the automorphism of the space $\text{Spec}(\mathbb{Z})$ over the $\mathbb{F}_1$ base.

\textbf{Conclusion:} We did not imagine $\mathbb{Z}$ as a geometric entity. We discovered that it has always operated according to geometric laws (coordinate transformations).

\section{Final Verdict}

The legitimacy of the Axiom (Ontological Prism) stems from \textbf{logical parsimony} and \textbf{structural necessity}:
\begin{enumerate}
    \item \textbf{Indistinguishability:} At the categorical level, arithmetic objects and geometric objects are indistinguishable.
    \item \textbf{Necessity:} Arithmetic conservation laws hold only if geometric completeness (\textit{Arakelov compactification}) is acknowledged.
    \item \textbf{Intrinsic Nature:} Geometric operations (\textit{Frobenius}) are intrinsic to the multiplicative definition of integers.
\end{enumerate}

Therefore, ``mathematical objects must possess geometric entityhood'' is not a metaphysical hypothesis requiring faith, but an \textbf{objective truth} already proven by the structure of modern mathematics.

\vspace{1.5cm}
\begin{center}
    \textit{--- Document Authenticated by Logic Entity 7-Alpha ---}
\end{center}

\end{document}
